---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r, include = FALSE}
knitr::opts_chunk$set(collapse  = TRUE,
                      comment   = "#>",
                      fig.path  = "man/figures/",
                      out.width = "100%")
```



# EpiverseTraceWorkshop


<!-- badges: start -->
<!-- badges: end -->


Research Compendium of the project **{{ PLEASE ADD A FEW WORDS }}**



### How to cite

Please cite this compendium as: 

```{r, echo = FALSE}
readCitationFile(file = "inst/CITATION")
```



### Content

This repository is structured as follow:

- [`data/`](https://github.com/emiel200/EpiverseTraceWorkshop/tree/master/data):
contains all raw data required to perform analyses

- [`analyses/`](https://github.com/emiel200/EpiverseTraceWorkshop/tree/main/analyses/):
contains R scripts to run each step of the workflow

- [`outputs/`](https://github.com/emiel200/EpiverseTraceWorkshop/tree/main/outputs):
contains all the results created during the workflow

- [`figures/`](https://github.com/emiel200/EpiverseTraceWorkshop/tree/main/figures):
contains all the figures created during the workflow

- [`R/`](https://github.com/emiel200/EpiverseTraceWorkshop/tree/main/R):
contains R functions developed especially for this project

- [`man/`](https://github.com/emiel200/EpiverseTraceWorkshop/tree/main/man):
contains help files of R functions

- [`DESCRIPTION`](https://github.com/emiel200/EpiverseTraceWorkshop/tree/main/DESCRIPTION):
contains project metadata (author, date, dependencies, etc.)

- [`make.R`](https://github.com/emiel200/EpiverseTraceWorkshop/tree/main/make.R):
main R script to run the entire project by calling each R script stored in the `analyses/` folder



### Usage

### Usage

First, clone this repository. You can follow [steps on creating a new Rstudio Project from a GitHub repository](https://www.epirhandbook.com/en/version-control-and-collaboration-with-git-and-github.html?q=clone#clone-from-a-github-repository). 

Then, run:

```{r eval = FALSE}
source("make.R")
```



### Notes

- All required packages, listed in the `DESCRIPTION` file, will be installed (if necessary)
- All required packages and R functions will be loaded
- Some analyses listed in the `make.R` might take time
